---
title: "Lab 00 - Hello IDS!"
author: "Duncan Hoyland"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Duncan Hoyland", "Charlie Franklin-WHite","Jamie Burrow", 
           "Dru Keiri", "Sean Wuang", "Annie Loi"),
  github_username = c("duncan-hoyland", "cfranklinwhite", "jamie-burrow", 
                      "squarehedge34", "sw-005", "aaaanniie"), 
  colour = c("seagreen", "blue", "blue", 
             "purple", "green", "blue"),
  hobby = c("rugby", "poker", "climbing", 
            "basketball", "gaming","gaming"),
  favourite_number = c(2, 2, 2, 6, 8, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Bar graph is showing farourite number of each team member against their username, with the bars being colour coded to show each team members favourite colour. Duncan has the coolest colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "git hub username", 
          y = "favourite number",
          title = "Super cool graph!")
```

Labs adds a title and axis label, pretty cool feature.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

There'd be so many different hobbies the data would be hard to easily interpret making it uninformative. Make it better by giving categories for people to select, restrcting the choice, grouping similar things such as sports. 
